%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   LaTeX File for Doctor (Master) Thesis of Tsinghua University
%   LaTeX + CJK     清华大学博士（硕士）论文模板
%   Based on Wang Tianshu's Template for XJTU
%   Version: 1.00
%   Last Update: 2003-09-12
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Copyright 2002-2003  by  Lei Wang (BaconChina)       (bcpub@sina.com)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   LaTeX File for xi'an Jiao Tong University
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Copyright 2001  by  Wang Tianshu    (tswang@asia.com)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\baselinestretch}{1.5}
\fontsize{12pt}{13pt}\selectfont

\chapter[ABSTRACT（英文摘要）]{\textsf{\textbf{Abstract}}}
\markboth{英~文~摘~要}{英~文~摘~要}
Due to endurance UAV capability, low cost, no casualties incomparable advantages of manned spacecraft
Potential, it has become a hot topic. By building FlightGear flight simulation platform to study four spin wing UAV flight control system, thereby improving the robustness of the flight control system.

First, this paper four-rotor UAV six degrees of freedom nonlinear flight dynamics modeling. In the modeling process
In this paper are considered from the perspective of the kinematics and mechanical point of two ways. In the kinematic equations derivation, Based on the theoretical basis of coordinate transformation, using quaternion rotation matrix conversion, in order to establish Kinematic equations. In mechanics equation derivation, based on the mechanical properties of four rotors, irrespective of four rotors Aerodynamic characteristics, the establishment of six degrees of freedom nonlinear equations. In the process of solving the model, based on the small disturbance Move assumptions, the nonlinear equation linearization, thereby solving the model.

Then, this paper build simulation platform, the establishment of three-dimensional visual simulation system based on FlightGear,Semi-physical simulation. In this paper, the use of C ++ programming Joystick Joystick data read, reads,
According to FlightGear programming through UDP communications, thereby performing flight attitude control. In the simulation platform To build the three-dimensional visualization of research is a very important part, you can exercise status and overall UAV Structure for visual display, enabling real-time display of UAV flight position and attitude change effects, increasing .Plus flight simulation authenticity. Flight simulation platform for vehicle test research has an important role,Not only the law can be summarized fly the aircraft, but also be able to assess the performance of the aircraft, reducing flight Risks and costs, improve flight safety.

Finally, on building simulation platform, simulated flight simulation effects. During the simulation,FlightGear software needs to be configured. Meanwhile, the paper also four-rotor flight .Improved control model is proposed to take feasibility flight control based on visual thinking, thus weakening people.The role of the entire control system, reduced human intervention to achieve autonomous flight.

\vspace{1em}
\noindent {\textbf{KEY WORDS:}} flight control model of six degrees of freedom, quaternion, three-dimensional visual simulation system, loop simulation
